Carbonate chemistry at Ny-Ålesund

### 2021-04-01 awipev-CO2.Rmd
refined K1K2

diff_table <- tibble(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), lueker, sulpis, papadimitriou, millero2002)

@@

# save elements for k1k2 report
k1k2_pco2_at <- list(mean_discrete = mean_discrete, const_choice = const_choice, tmp2 = tmp2,
             errors_pco2_at = errors_pco2_at, diff_table = diff_table, 
             diff_ls_quant = diff_ls_quant)
save(k1k2_pco2_at, file="reports/k1k2_pco2_at.RData")
```

@@

Here we compare pH measured spectrophotometrically with pH calculated from pCO2 and AT using various formulations of K1 and K2. All pH values were normalized to a temperature of 4°C. The absolute differences are generally large, up to `r round(max(abs(diff_table[, 2:5])), digits=3)` pH units. In general, all formulations overestimate spectrophotometric pH. pH calculated using the formulation of Papadimitriou et al. (2018) is closer to measured pH, with a mean difference of `r round(diff_table[4, 4], digits=3)` pH units. This difference is `r abs(round(diff_table[4, 4]/errors_pco2_at$pH, digits=1))` times larger than the uncertainty for pH calculated from pCO2 and AT according to seacarb (`r round(errors_pco2_at$pH, digits=3)`).
`r knitr::kable(diff_table, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with pCO2 and AT using different formulations for K1 and K2.", format = "simple")`
`r include_graphics("figures/k1k2_all_pco2_at.png")`

@@

diff_table <- tibble(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), lueker, sulpis, papadimitriou, millero2002)

@@

# save elements for k1k2 report
k1k2_at_ct <- list(mean_discrete = mean_discrete, const_choice = const_choice, tmp2 = tmp2,
             errors_pco2_at = errors_pco2_at, diff_table = diff_table, 
             diff_ls_quant = diff_ls_quant)
save(k1k2_at_ct, file="reports/k1k2_at_ct.RData")
```
Here we compare pH measured spectrophotometrically with pH calculated from AT and CT using various formulations of K1 and K2. All pH values were normalized to a temperature of 4°C. The absolute differences are generally large, up to `r round(max(abs(diff_table[, 2:5])), digits=3)` pH units. In general, all formulations overestimate spectrophotometric pH. pH calculated using the formulation of Papadimitriou et al. (2018) is closer to measured pH, with a mean difference of `r round(diff_table[4, 4], digits=3)` pH units. This difference is `r abs(round(diff_table[4, 4]/errors_at_ct$pH, digits=1))` times larger than the uncertainty for pH calculated from AT and CT according to seacarb (`r round(errors_at_ct$pH, digits=3)`).

`r knitr::kable(diff_table, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with pCO2 and AT using different formulations for K1 and K2.", format = "simple")`
`r include_graphics("figures/k1k2_all_at_ct.png")`

>>>>

diff_table_pco2_at <- tibble(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), lueker, sulpis, papadimitriou, millero2002)

@@

# save elements for k1k2 report
k1k2_pco2_at <- list(mean_discrete = mean_discrete, const_choice = const_choice, tmp2 = tmp2,
             errors_pco2_at = errors_pco2_at, diff_table_pco2_at = diff_table_pco2_at, 
             diff_ls_quant = diff_ls_quant)
save(k1k2_pco2_at, file="reports/k1k2_pco2_at.RData")
```

@@

Here we compare pH measured spectrophotometrically with pH calculated from pCO2 and AT using various formulations of K1 and K2. All pH values were normalized to a temperature of 4°C. The absolute differences are generally large, up to `r round(max(abs(diff_table_pco2_at[, 2:5])), digits=3)` pH units. In general, all formulations overestimate spectrophotometric pH. pH calculated using the formulation of Papadimitriou et al. (2018) is closer to measured pH, with a mean difference of `r round(diff_table_pco2_at[4, 4], digits=3)` pH units. This difference is `r abs(round(diff_table_pco2_at[4, 4]/errors_pco2_at$pH, digits=1))` times larger than the uncertainty for pH calculated from pCO2 and AT according to seacarb (`r round(errors_pco2_at$pH, digits=3)`).
`r knitr::kable(diff_table_pco2_at, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with pCO2 and AT using different formulations for K1 and K2.", format = "simple")`
`r include_graphics("figures/k1k2_all_pco2_at.png")`

@@

diff_table_at_ct <- tibble(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), lueker, sulpis, papadimitriou, millero2002)

@@

# save elements for k1k2 report
k1k2_at_ct <- list(errors_at_ct = errors_at_ct,
                   diff_table_at_ct = diff_table_at_ct)
save(k1k2_at_ct, file="reports/k1k2_at_ct.RData")
```
Here we compare pH measured spectrophotometrically with pH calculated from AT and CT using various formulations of K1 and K2. All pH values were normalized to a temperature of 4°C. The absolute differences are generally large, up to `r round(max(abs(diff_table_at_ct[, 2:5])), digits=3)` pH units. In general, all formulations overestimate spectrophotometric pH. pH calculated using the formulation of Papadimitriou et al. (2018) is closer to measured pH, with a mean difference of `r round(diff_table_at_ct[4, 4], digits=3)` pH units. This difference is `r abs(round(diff_table_at_ct[4, 4]/errors_at_ct$pH, digits=1))` times the uncertainty for pH calculated from AT and CT according to seacarb (`r round(errors_at_ct$pH, digits=3)`). The differences found with the other formulations are, on average, slightly lower than the uncertainty for pH calculated from AT and CT according to seacarb.

`r knitr::kable(diff_table_at_ct, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with AT and CT using different formulations for K1 and K2.", format = "simple")`
`r include_graphics("figures/k1k2_all_at_ct.png")`
